\section{Glossary}

{\Large\textbf{A}\par}
\textbf{Application Logic}\\
Application Logic is any logic that is specific to some application.

{\Large\textbf{B}\par}
\textbf{Business Logic}\\
It is the processing logic, in the form of source code, which manages the communication between a user interface and a database. It therefore contains the information that defines or they bind the way a company operates.

{\Large\textbf{C}\par}
\textbf{CSV}\\
CSV (comma-separated values) is a simple file format used to store tabular data, such as a spreadsheet or database.

{\Large\textbf{D}\par}
\textbf{DOM}\\
The Document Object Model (DOM) is a platform and language-neutral interface that allows programs and scripts to dynamically access and update the content, structure, and style of a document.

{\Large\textbf{L}\par}
\textbf{Linear Regression (LR)}\\
Linear regression (LR) is a linear approach to modeling the relationship between a scalar response (or dependent variable) and one or more explanatory variables (or independent variables). The case of one explanatory variable is called simple linear regression.

{\Large\textbf{G}\par}
\textbf{Grafana}\\
Grafana is a multi-platform open source analytics and interactive visualization web application. It provides charts, graphs, and alerts for the web when connected to supported data sources. It is expandable through a plug-in system. End users can create complex monitoring dashboards using interactive query builders.

\textbf{GUI}\\
A graphical user interface (GUI) is an interface through which a user interacts with electronic devices such as computers, hand-held devices and other appliances. 

{\Large\textbf{J}\par}
\textbf{JavaScript}\\
JS is a programming language that conforms to the ECMAScript specification. JavaScript is high-level, often just-in-time compiled, and multi-paradigm. 

\textbf{JSON}\\
JSON (JavaScript Object Notation) is a lightweight data-interchange format. It is easy for machines to parse and generate.

\textbf{JSX}\\
JSX is an extension of the JavaScript language based on ES6, and is translated into regular JavaScript at runtime.

{\Large\textbf{M}\par}
\textbf{Machine learning}\\
Machine learning (ML) is the study of computer algorithms that improve automatically through experience. Machine learning algorithms, such as LR or SVM, build a mathematical model based on sample data, known as "training data", in order to make predictions or decisions without being explicitly programmed to do so.

{\Large\textbf{N}\par}
\textbf{Node.js}\\
Node.js is an open-source, cross-platform, JavaScript runtime environment that executes JavaScript code outside a web browser. Node.js lets developers use JavaScript to write command line tools and for server-side scripts to produce dynamic web page content before the page is sent to the user's web browser.

\textbf{NPM}\\
NPM (Node Package Manager) is a package manager for the JavaScript programming language. It is the default package manager for the JavaScript runtime environment Node.js.

{\Large\textbf{O}\par}
\textbf{OS}\\
An Operating System (OS) is an interface between a computer user and computer hardware. An operating system is a software which performs all the basic tasks like file management, memory management, process management, handling input and output, and controlling peripheral devices.

{\Large\textbf{P}\par}
\textbf{Package}\\
A package (java package) is used to group related classes. They are used to avoid name conflicts, and to write a better maintainable code. 

\textbf{Presentation Logic}\\
The presentation logic of an application is where occurs almost of all interactions with the end user. Manages the reception of user inputs and the presentation of the output of the application to the latter.

{\Large\textbf{R}\par}
\textbf{React}\\
React is a JavaScript library for building user interfaces.

{\Large\textbf{S}\par}
\textbf{Support Vector Machine (SVM)}\\
In machine learning, Support Vector Machines (SVM) are supervised learning models with associated learning algorithms that analyze data used for classification and regression analysis.

{\Large\textbf{T}\par}
\textbf{Typescript}\\
TypeScript is a typed superset of JavaScript that compiles to plain JavaScript.

