\section{Technologies}
\subsection{ESLint}
ESLint is a plugin used for code static analysis, so it checks for JavaScript syntax errors.

\subsection{InfluxDB}
InfluxDB it's an open source time series database which is used to store and manage data inside the Prediction Plugin. 

\subsection{NodeJS}
NodeJS it's a runtime environment that execute JavaScript code outside a web browser. NodeJS it's useful for the tool's developing.

\subsection{NPM}
NPM or Node Package Manager it's used to manage dependencies and build automation. All its functionalities are available by the presence of the file package.json. In this project there are two copies of it because each product needs a dedicated package.json file. So tool's configuration and management are independent from those required for the plugin.

\subsection{React}
React it's a JavaScript library for building user interfaces for both plugin and tool.

\subsection{JSX}
JSX it's an extension of JavaScript language syntax. This extension helps to create HTML components for the Training Tool.

\subsection{TypeScript}
TypeScript it's a JavaScript superset that provides static typing to the language. Since Grafana is actually based on this language, TypeScript is used to develop the plugin.

\subsection{JSON}
JSON it's an open standard file format used to store the training data obtained from the Training Tool. So JSON files allows to pass data between tool and plugin.

\subsection{CSV}
CSV it's a file format used to store data for tool's training tests.

\subsection{Travis CI}
Travis i is an hosted continuous integration service used to build and test software hosted on GitHub.

\subsection{Linear Regression}
The Linear regression it's a linear approach to modelling the relationship between dependent and independent variable through points setted on a plan.

\subsection{Support Vector Machine}
A Support Vector Machine it's a supervised learning model used in machine learning. With a SVM input data that are analysed  and classified in two different classes.
 